### 2016-09-30 notions.tex
cheers

\section{Security Notions}
\label{sec:security-notions}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.
In addition to correctness, we establish notions of privacy for
set-multiplicity data structures.
\jnote{I would call it ``soundness'' rather than ``correctness.'' But if you disagree,
just remove this comment and we'll go with correctness.}

\tsnote{flesh out}

@@

In this experiment we track the time complexity (relative to some
model of computation) and query complexity (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\setprim,r}{A} = \Prob{\ExpCorrect{\setprim,r}{A}=1}$.
\tsnote{drop} Overloading notation, we write $\AdvCorrect{\setprim,r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say a
data structure~$\setprim$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\setprim,r}{t,q} \leq \epsilon$.

\todo{Explain that the case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
where finding the first false positive is hard but then the rest are easy; can have
a scheme where finding one false positive is easy but finding more is hard (e.g.,
because there do not exist
any more). Note that the [NY15] definition does not capture this at all.}

@@

Our semantic-security definition is based on the simulation paradigm (see Figure~\ref{fig:privacy-ss}).
\jnote{Here it would not be hard to write the definition for general data structures, not
specifically set-multiplicity data structures.}
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
public information $\pubaux$ that results from running $\Rep(S)$.
%\footnote{We do not give $A$ an oracle for issuing queries;
%since $A$ knows the set~$S$, such an oracle would be superfluous.
%\jnote{Interestingly,
%if we provided a query oracle in the real world and an oracle that returns the correct
%answer in the simulated world, then the definition seems to imply
%correctness also.}}
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
function~${\sf leak}$.
For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
we define the advantage
$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim} \bydef
\left| \Prob{\ExpPrivSSreal{\setprim}{A}=1} -
\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \right|$.
Informally, a scheme $\setprim$ is secure with respect to some leakage function ${\sf leak}$
if for all efficient $A$ there is a simulator $\Sim$ such that
$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim}$ is small.
Intuitively, this means that the public portion
$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
\jnote{The definition
as stated does not really work well in the presence of (programmable) random oracles.}
\jnote{In the current definition there is (intentionally) no bound on the simulator's
running time.}

\begin{figure}[tp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\setprim}{A}$}\\
$S \getsr A$ \\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}}{A, \Sim}$}\\
$S \getsr A$\\
$\pubaux \getsr \Sim({\sf leak}(S))$ \\
return $A(\pubaux)$\\
}
}
\caption{Experiments for the ``semantic-security'' privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

%\begin{figure}[hbtp]
%\centering
%\fpage{.6}{
%\hpagess{.5}{.45}
%{
%\experimentv{$\ExpPrivSSreal{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$ \\
%$(\pubaux,\privaux) \getsr \Rep(S)$\\
%return $A(S,\pubaux)$\\
%}
%%
%{
%\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}, \distr{}{}}{A, \Sim}$}\\
%$S \getsr \distr{}{}$\\
%$\pubaux \getsr \Sim({\sf leak}(S))$ \\
%return $A(S,\pubaux)$\\
%}
%}
%\caption{Experiments for the ``distibutional semantic-security'' privacy
%  definition.}
%\label{fig:privacy-dss}
%\end{figure}
\todo{A simple theorem that says if $\privaux=\emptystring$ then
  SS-privacy is unachievable for any leakage other than $\leak(S)=S$?
It's at least worth a highlighted remark, I think.  Currently it is a
remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}

\heading{Relationships between the notions.}
Intuition suggests that semantic security should imply one-wayness. And, indeed, this is
the case---provided one is careful with the technical details.
For a distribution ${\cal D}$
over subsets of some universe ${\cal X}$, define
\[\tilde H_\infty({\cal D} \mid {\sf leak}) \bydef -\log \sum_{r \in R} \Pr_{S \getsr {\cal D}}[{\sf leak}(S)=r] \cdot
\max_{x \in {\cal X}} \Pr_{S \getsr {\cal D}}[x \in S \mid {\sf leak}(S)=r].\]

>>>>

\section{Security Notions}
\label{sec:security-notions}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.
In addition to correctness, we establish notions of privacy for
set-multiplicity data structures.
\jnote{I would call it ``soundness'' rather than ``correctness.'' But if you disagree,
just remove this comment and we'll go with correctness.}\tsnote{I
think stick with correctness, since that's the what's used in NY and
in classical literature on BFs.  Or something entirely different, but
I don't know what.  But using ``soundness'' would seem to overload yet
another term, no?}

\fixme{Do we say that all notions can be extended to the ROM by giving
all all algorithms to a RO~$H$?  Is this true for the SS-privacy
notion?  (It seems to make sense elsewhere.)}

\todo{flesh out opening text}

@@

In this experiment we track the time complexity~$t$ (relative to some
model of computation) and query complexity~$q$ (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\setprim,r}{A} = \Prob{\ExpCorrect{\setprim,r}{A}=1}$.
%\tsnote{drop} Overloading notation, we write $\AdvCorrect{\setprim,r}{t,q}$ for the maximum over
%all~$t$-time adversaries that ask at most~$q$ queries. We say a
%data structure~$\setprim$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\setprim,r}{t,q} \leq \epsilon$.

\todo{[JON] Explain that the case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
where finding the first false positive is hard but then the rest are easy; can have
a scheme where finding one false positive is easy but finding more is hard (e.g.,
because there do not exist
any more). Note that the [NY15] definition does not capture this at all.}

@@

Our semantic-security definition is based on the simulation paradigm (see Figure~\ref{fig:privacy-ss}).
\jnote{Here it would not be hard to write the definition for general data structures, not
specifically set-multiplicity data structures.}
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
public information $\pubaux$ that results from running $\Rep(S)$.
%\footnote{We do not give $A$ an oracle for issuing queries;
%since $A$ knows the set~$S$, such an oracle would be superfluous.
%\jnote{Interestingly,
%if we provided a query oracle in the real world and an oracle that returns the correct
%answer in the simulated world, then the definition seems to imply
%correctness also.}}
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
function~${\sf leak}$.
For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
we define the advantage
$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim} \bydef
\left| \Prob{\ExpPrivSSreal{\setprim}{A}=1} -
\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \right|$.
Informally, a scheme $\setprim$ is secure with respect to some leakage function ${\sf leak}$
if for all efficient $A$ there is a simulator $\Sim$ such that
$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim}$ is small.
Intuitively, this means that the public portion
$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
\jnote{The definition
as stated does not really work well in the presence of (programmable) random oracles.}
\jnote{In the current definition there is (intentionally) no bound on the simulator's
running time.}
\todo{Mention why giving a Test oracle to A doesn't seem to help.}
\begin{figure}[tp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\setprim}{A}$}\\
$S \getsr A$ \\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}}{A, \Sim}$}\\
$S \getsr A$\\
$\pubaux \getsr \Sim({\sf leak}(S))$ \\
return $A(\pubaux)$\\
}
}
\caption{Experiments for the ``semantic-security'' privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

%\begin{figure}[hbtp]
%\centering
%\fpage{.6}{
%\hpagess{.5}{.45}
%{
%\experimentv{$\ExpPrivSSreal{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$ \\
%$(\pubaux,\privaux) \getsr \Rep(S)$\\
%return $A(S,\pubaux)$\\
%}
%%
%{
%\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}, \distr{}{}}{A, \Sim}$}\\
%$S \getsr \distr{}{}$\\
%$\pubaux \getsr \Sim({\sf leak}(S))$ \\
%return $A(S,\pubaux)$\\
%}
%}
%\caption{Experiments for the ``distibutional semantic-security'' privacy
%  definition.}
%\label{fig:privacy-dss}
%\end{figure}
\todo{A simple theorem that says if $\privaux=\emptystring$ then
  SS-privacy is unachievable for any leakage other than $\leak(S)=S$?
It's at least worth a highlighted remark, I think.  Currently it is a
remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}
\todo{Since we mention what happens with $\privaux=\emptystring$, also
mention what happens with $\pubaux=\emptystring$ :)}
\heading{Relationships between the notions.}
Intuition suggests that semantic security should imply one-wayness. And, indeed, this is
the case---provided one is careful with the technical details.
For a distribution ${\cal D}$
over subsets of some universe ${\cal X}$, define
\[\tilde H_\infty({\cal D} \mid {\sf leak}) \bydef -\log \sum_{r \in R} \Pr_{S \getsr {\cal D}}[{\sf leak}(S)=r] \cdot
\max_{x \in {\cal X}} \Pr_{S \getsr {\cal D}}[x \in S \mid {\sf leak}(S)=r].\]

### 2016-09-30 results.tex
cheers

\begin{figure}[t]
\centering
\fpage{.425}
{
\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{Attack for garbled Bloom filters with public~$M$. }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
details, a GBF is like a classical Bloom filter, but
rather than storing a bit 1 at the indices determined by $H_j(x)$, the
GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
and xoring together the strings stored at the indicated positions
recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
algorithms in Figure~\ref{fig:gbf}.

@@

\heading{Privacy. }
We observe i
\todo{Public M, ROM (no, empty priv)}\tsnote{one-wayness suffers the same
  attack as correctness, I think?}

>>>>

\begin{figure}[t]
\centering
\fpage{.425}
{
\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{Correctness attack for garbled Bloom filters with public~$M$. }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
details, a GBF is like a classical Bloom filter, but
rather than storing a bit 1 at the indices determined by $H_j(x)$, the
GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
and xoring together the strings stored at the indicated positions
recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
algorithms in Figure~\ref{fig:gbf}.

@@

\heading{Privacy. }
We observe immediately that when~$\pubaux=\langle M \rangle$ the GBF cannot be SS-private (in the ROM) because $\privaux=\emptystring$.  In fact, it is easy to see that the correctness attack just given works as a privacy attack, too, with small modifications.  In particular, the attacker cannot check that the reconstructed $x \not\in S$.

\todo{Public M, ROM (no, empty priv)}\tsnote{one-wayness suffers the same
  attack as correctness, I think?}
